Exercise 1: Software Architecture Description of the HS07 System

### 2008-02-06 trunk/SAiP/Module1/H1/doc/paper.tex
Comment about scope and context added.

\begin{description}
	\item[Clause 5.1 Architectural documentation] This report does not include a change history
		and a glossary as defined in the recommended practice. (XXX: scope, context?)
	\item[Clause 5.2 Identification of stakeholders and concers] The stakeholders of this system and
		their precise concerns have not been identified in this report. This must be done in order to
		conform to the recommended practice.
	\item[Clause 5.3 Selection of architectural viewpoints] The viewpoints used in this architectural
		description are defined in \cite{christensen2004archdesc}.
	\item[Clause 5.4 Architectural views] This report contains the following architectural views: Module
		View, Component \& Connector View and Allocation View.
	\item[Clause 5.5 Consistency among architectural views] There is no consistency check across the views
		in this report as specified in the recommended practice.
	\item[Clause 5.6 Architectural rationale] There is no rationale for the architectural decisions
		that have made in this report.
\end{description}

>>>>

\begin{description}
	\item[Clause 5.1 Architectural documentation] This report does not include a description of the
		scope of this document, a change history and a glossary as defined in the recommended practice.
		The context is briefly covered in the introduction.
	\item[Clause 5.2 Identification of stakeholders and concers] The stakeholders of this system and
		their precise concerns have not been identified in this report. This must be done in order to
		conform to the recommended practice.
	\item[Clause 5.3 Selection of architectural viewpoints] The viewpoints used in this architectural
		description are defined in \cite{christensen2004archdesc}.
	\item[Clause 5.4 Architectural views] This report contains the following architectural views: Module
		View, Component \& Connector View and Allocation View.
	\item[Clause 5.5 Consistency among architectural views] There is no consistency check across the views
		in this report as specified in the recommended practice.
	\item[Clause 5.6 Architectural rationale] There is no rationale for the architectural decisions
		that have made in this report.
\end{description}
